### 2021-06-08 paper/report.tex
Reformat.

% Reports (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance. Reports should include an abstract, an introductory paragraph, up to four figures or tables, and about 30 references. Materials and Methods should be included in supplementary materials, which should also include information needed to support the paper's conclusions.

@@

% The manuscript should start with a brief introduction describing the paper’s significance. The introduction should provide sufficient background information to make the article intelligible to readers in other disciplines, and sufficient context that the significance of the experimental findings is clear.

@@

    \floatfoot{\noindent
        Note: ...
    }
\end{figure}

@@

Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and
of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially
recorded cases; the \replaced[id=HM]{color}{blue?} line in
Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index \citep{Hale2020},
which tracks the tightness of non-pharmaceutical interventions. We transform the index so
that lower values represent higher levels of restrictions. A value of zero means all
measures incorporated in the index are turned on. The value 1 represents the situation of
mid-September, where half of all restrictions incorporated in the index are
active.\comment[id=HM]{Need to find version of index with a couple of measures, probably
need the API access...}. In the six weeks between mid September and mid October, cases
increased by a factor of 3.\comment[id=K]{In the next iteration all empirical data is
in the figures/results/tables/empirical\_analogues.csv}
% the week of Sep 13 had an incidence of 12.4, the week of Oct 18 had 51.
Restrictions were somewhat tightened in mid-October and again in early November. New
infections remained constant throughout November, before rising again in December.

@@

        Sources: ...
    }

@@

    The decomposition is based on Shapley values where the individual contribution of a channel is its average contribution over different sizes of coalitions (combinations with other channels). The individual contribution to a coalition is the difference between the effect size of the coalition with the particular channel and without.
    }
\end{figure}

Until mid-March, there is no visible difference between the different scenarios. Seasonality hardly changes, and only few vaccinations or rapid tests were administered. Even thereafter, the effect of the vaccination campaign is surprisingly small at first sight. Whether considering recorded or total infections, the final level is always the highest in case the vaccination campaign had been running in isolation (red lines). The Shapley value decomposition shows that vaccinations contribute about 15\%\comment[id=HM]{check!} to the cumulative difference between scenarios. Reasons for the slow this are the slow start---10\% of the population was vaccinated in XX date, 20\% in mid-April\comment[id=HM]{(check!)}---and the focus on older individuals. These groups contribute less to the spread of the disease than others due to a lower number of contacts, see~\ref{fig:assortativity}. It is important to note that the initial focus of the campaign was to prevent deaths and severe disease; the case fatality was rate considerably lower during the third wave when compared to the second.\comment[id=HM]{Calculate N deaths / N cases, for RKI data 1 October - 31 Jan vs. 1 Mar - 31 May}. It is important to note that by the end of our study period, when first-dose vaccination rates reached around 40\% of the population, the numbers of new cases would have started to decline.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
        \caption{{\small Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/}
        \caption{{\small Effects of different work scenarios after Easter}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex

@@

    \floatfoot{\noindent
        Note: All aggregates; See S.XXX for statistics by age group and by geographical region.
    }

@@

% All data must be shown either in the main text or in the Supplementary Materials or must be available in an established database with accession details provided in the acknowledgements section.

% References to unpublished materials are not allowed to substantiate significant conclusions of the paper.

>>>>

% Reports (up to ~2500 words including references, notes and captions–corresponds to ~3
% printed pages in the journal) present important new research results of broad
% significance. Reports should include an abstract, an introductory paragraph, up to
% four figures or tables, and about 30 references. Materials and Methods should be
% included in supplementary materials, which should also include information needed to
% support the paper's conclusions.

@@

% The manuscript should start with a brief introduction describing the paper’s
% significance. The introduction should provide sufficient background information to
% make the article intelligible to readers in other disciplines, and sufficient context
% that the significance of the experimental findings is clear.

@@

    \floatfoot{\noindent Note: ...}
\end{figure}

@@

Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and
of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially
recorded cases; the \replaced[id=HM]{color}{blue?} line in
Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index \citep{Hale2020},
which tracks the tightness of non-pharmaceutical interventions. We transform the index
so that lower values represent higher levels of restrictions. A value of zero means all
measures incorporated in the index are turned on. The value 1 represents the situation
of mid-September, where half of all restrictions incorporated in the index are
active.\comment[id=HM]{Need to find version of index with a couple of measures, probably
need the API access...}. In the six weeks between mid September and late October, cases
increased by a factor of XX.\comment[id=K]{In the next iteration all empirical data is
in the figures/results/tables/empirical\_analogues.csv}
% the week of Sep 13 had an incidence of 12.4, the week of Oct 18 had 51.
Restrictions were somewhat tightened in mid-October and again in early November. New
infections remained constant throughout November, before rising again in December.

@@

        Sources: ...}

@@

    The decomposition is based on Shapley values where the individual contribution of a
    channel is its average contribution over different sizes of coalitions (combinations
    with other channels). The individual contribution to a coalition is the difference
    between the effect size of the coalition with the particular channel and without.}
\end{figure}

Until mid-March, there is no visible difference between the different scenarios.
Seasonality hardly changes, and only few vaccinations or rapid tests were administered.
Even thereafter, the effect of the vaccination campaign is surprisingly small at first
sight. Whether considering recorded or total infections, the final level is always the
highest in case the vaccination campaign had been running in isolation (red lines). The
Shapley value decomposition shows that vaccinations contribute about
15\%\comment[id=HM]{check!} to the cumulative difference between scenarios. Reasons for
this are the slow start---it took until 24~March until 10\% of the population had
received their first vaccination, the 20\% mark was reached on April 19th ---and the
focus on older individuals. These groups contribute less to the spread of the disease
than others due to a lower number of contacts, see~\ref{fig:assortativity}. It is
important to note that the initial focus of the campaign was to prevent deaths and
severe disease; the case fatality was rate considerably lower during the third wave when
compared to the second (4.4\% between October and February and 1.4\% between March and
June). It is important to note that by the end of our study period, when first-dose
vaccination rates reached around 40\% of the population, the numbers of new cases would
have started to decline.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
        \caption{{\small Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=0.9
        % \textwidth]{../figures/results/figures/scenario_comparisons/}
        \caption{{\small Effects of different work scenarios after Easter}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex

@@

    \floatfoot{\noindent Note: All aggregates; See S.XXX for statistics by age group and
        by geographical region.}

@@

% All data must be shown either in the main text or in the Supplementary Materials or
% must be available in an established database with accession details provided in the
% acknowledgements section.

% References to unpublished materials are not allowed to substantiate significant
% conclusions of the paper.
